---
title: "Myanmar Conflict: Spatial Analysis"
author: "Ming Thet & Htet Myat"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: readable
---


```{r}
library(flexdashboard)
library(shiny)
library(sf)
library(spdep)
library(spatialreg)
library(ggplot2)
library(dplyr)
library(readxl)
library(leaflet)
library(tidyr)
library(ggcorrplot)
library(stargazer)
library(tmap)
library(knitr)
library(janitor)
```

```{r}
file_name <- "C:/Users/Htet Myat/Desktop/Spring 2026/Spatial Econometrics/spatialgroupproject/Aggregated_dataset (1).xlsx"

# Using read_excel instead of read.csv
df <- read_excel(file_name)
colnames(df) <- make.names(colnames(df))

```



```{r}

df

```
```{r}

str(df)

```




```{r Data Cleaning}

# Fix skewness by log-transforming fatalities (log1p handles 0s)
df$log_fatalities <-as.numeric(log1p(df$fatalities))
```


```{r}

library(tidyverse)

# 1. Identify and summarize all numeric variables
# We exclude latitude and longitude as they are coordinates
plot_data <- df %>%
  select(where(is.numeric)) %>%
  select(-any_of(c("latitude", "longitude"))) %>%
  summarise(across(everything(), sum, na.rm = TRUE)) %>%
  pivot_longer(everything(), names_to = "Variable", values_to = "Total") %>%
  arrange(Total) # Sorting helps readability

# 2. Clean the names for display (Optional but recommended)
# This replaces dots with spaces to make it look like your Excel file
plot_data$Clean_Name <- gsub("\\.", " ", plot_data$Variable)

# 3. Generate the Horizontal Barplot
ggplot(plot_data, aes(x = reorder(Clean_Name, Total), y = Total)) +
  geom_bar(stat = "identity", fill = "#4682B4") + 
  coord_flip() +  # Makes it horizontal
  theme_minimal() +
  labs(
    title = "Comparison of All Numerical Variables",
    subtitle = "Aggregated total counts for conflict metrics",
    x = "", 
    y = "Total (Sum)"
  ) +
  theme(
    axis.text.y = element_text(size = 9), # Adjust size to prevent crowding
    plot.title = element_text(face = "bold"),
    panel.grid.minor = element_blank()
  )

```


```{r}
# --- 3. CONVERT TO SPATIAL OBJECT ---
sf_data <- st_as_sf(df, coords = c("longitude", "latitude"), crs = 4326) %>%
           st_jitter(amount = 0.0001)

```

```{r}

# --- 4. BUILD WEIGHTS (CRITICAL STEP) ---

# We build the weights on the FINAL sf_data so the lengths ARE identical
coords <- st_coordinates(sf_data)
knn <- knearneigh(coords, k = 5)
nb <- knn2nb(knn)
listw_knn <- nb2listw(nb, style = "W")

```
```{r}

print(paste("Final Data Rows:", nrow(sf_data)))
print(paste("Final Weights Rows:", length(listw_knn$neighbours)))

```

```{r}

# Summary table of fatalities from the sample
stats_summary <- df %>%
  summarise(
    Observations = n(),
    Mean_Fatalities = mean(fatalities, na.rm = TRUE),
    Median_Fatalities = median(fatalities, na.rm = TRUE),
    Std_Dev = sd(fatalities, na.rm = TRUE)
  )
kable(stats_summary, caption = "Summary Statistics of Fatalities (Sample N=4200)", digits = 2)

```


```{r}
# Histogram of log-transformed fatalities to show corrected distribution
ggplot(df, aes(x = log_fatalities)) +
  geom_histogram(fill = "#d73027", color = "white", bins = 35) +
  labs(title = "Log-Distribution of Fatalities", 
       subtitle = "Corrected for skewness (18.59)",
       x = "Log(Fatalities + 1)", y = "Frequency") +
  theme_minimal()

```

```{r}

# Using your original column names
eda_vars <- df %>%
  select(fatalities, Political.Violence.Frequency, 
         Air.drone.strike..Sub.event., Shelling.artillery.missile.attack..Sub.event., 
         Battles..Event., Civilian.targeting)

corr <- round(cor(eda_vars, use = "complete.obs"), 2)

ggcorrplot(corr, hc.order = TRUE, type = "lower",
           lab = TRUE, lab_size = 3, method="circle", 
           colors = c("#6D9EC1", "white", "#E46726"),
           title="Correlation Matrix of Conflict Features",
           ggtheme=theme_minimal())
```
```{r}
library(rnaturalearth)
library(rnaturalearthdata)
library(ggplot2)
library(sf)

# Fetch Myanmar administrative boundary (State/Region level)
# Change scale to 'medium' to avoid the rnaturalearthhires requirement
myanmar_boundary <- ne_countries(scale = 110, country = "Myanmar", returnclass = "sf")
library(tmap)

# 1. Force the scaling and margins to favor a larger map
tmap_options(component.autoscale = FALSE)

# 2. Build the map with state lines
map_final <- tm_shape(myanmar_boundary) +
  tm_polygons(col = "#fdfdfd", 
              border.col = "black", 
              lwd = 0.8) +          # <--- Thicker black lines for state borders
tm_shape(sf_data) +
  tm_dots(col = "fatalities", 
          palette = c("#D3D3D3", "#FF69B4", "#FFCC00", "#FF8C00", "#FF0000"), 
          size = 0.4,               # <--- Increased dot size on the map
          style = "fixed", 
          breaks = c(-Inf, 0.9, 5, 20, 100, Inf),
          labels = c("0 Fatalities", "1 - 5 (Pink)", "6 - 20 (Light Orange)", 
                     "21 - 100 (Dark Orange)", "100+ (Red)"),
          alpha = 0.85,
          title = "Conflict Intensity") +
          
# 3. Layout: Forcing the square boxed legend and making everything bigger
  tm_layout(main.title = "Myanmar Conflict Spatial Intensity",
            main.title.size = 1.2,
            inner.margins = c(0, 0, 0, 0), # <--- Removes empty space to make map bigger
            legend.outside = TRUE,
            legend.outside.position = "right",
            legend.symbol.type = "square", 
            legend.symbol.size = 4.0,      # <--- Massive squares in the legend
            legend.text.size = 0.9,
            legend.title.size = 1.1,
            legend.bg.color = "white",
            legend.frame.color = "black", 
            legend.frame.lwd = 1.5,
            frame = FALSE)

# 4. Display
map_final
```






```{r}

leaflet(sf_data) %>%
  addProviderTiles(providers$CartoDB.Positron) %>%
  addCircleMarkers(
    radius = ~sqrt(fatalities + 1) * 1.5,
    color = ~ifelse(fatalities > median(fatalities), "#d73027", "#4575b4"),
    stroke = FALSE, 
    fillOpacity = 0.6,
    label = ~location,
    popup = ~paste0(
      "<b>Location:</b> ", location, "<br>",
      "<b>Fatalities:</b> ", fatalities, "<br>",
      "<b>Airstrikes:</b> ", Air.drone.strike..Sub.event., "<br>",
      "<b>Shelling/Artillery:</b> ", Shelling.artillery.missile.attack..Sub.event.
    )
  ) %>%
  addLegend(
    position = "bottomright",
    colors = c("#d73027", "#4575b4"),
    labels = c("Above Median Fatalities (High Intensity)", "Below Median Fatalities (Low Intensity)"),
    title = "Conflict Intensity",
    opacity = 0.8
  )

```

```{r}

# Global Moran's I on Log-Fatalities
moran_fatalities <- moran.test(as.numeric(sf_data$log_fatalities), listw_knn)
print("--- Global Moran's I: Log-Fatalities ---")
print(moran_fatalities)

# Global Moran's I on Air/Drone Strikes
moran_air <- moran.test(sf_data$Air.drone.strike..Sub.event., listw_knn)
print("--- Global Moran's I: Air/Drone Strikes ---")
print(moran_air)

# LISA Hotspot Identification
local_m <- localmoran(as.numeric(sf_data$log_fatalities), listw_knn)
sf_data$quadrant <- "Non-Significant"
mean_log_fat <- mean(sf_data$log_fatalities)
sf_data$quadrant[local_m[,5] < 0.05 & sf_data$log_fatalities > mean_log_fat] <- "Hotspot (High-High)"
sf_data$quadrant[local_m[,5] < 0.05 & sf_data$log_fatalities < mean_log_fat] <- "Coldspot (Low-Low)"

```

```{r}

ggplot(sf_data) +
  geom_sf(aes(color = quadrant), size = 1.2) +
  scale_color_manual(values = c("Hotspot (High-High)" = "red", 
                                "Coldspot (Low-Low)" = "blue", 
                                "Non-Significant" = "grey85")) +
  theme_void() +
  labs(title = "LISA Cluster Map: Significant Fatalities Hotspots")


```

```{r}

library(tmap)

# 1. Tidy the data for faceting
sf_tidy <- sf_data %>%
  pivot_longer(
    cols = c(Battles..Event., Air.drone.strike..Sub.event., 
             Shelling.artillery.missile.attack..Sub.event., Violence.against.civilians..Event.),
    names_to = "event_category",
    values_to = "event_count"
  ) %>%
  # Filter to show only where an event actually happened
  filter(event_count > 0)

# 2. Plot with facets
tmap_mode("plot")
tm_shape(sf_tidy) +
  tm_bubbles(size = "fatalities", 
             col = "event_category", 
             palette = "Set1",
             alpha = 0.6, 
             scale = 1.5,
             title.size = "Fatalities") +
  tm_facets(by = "event_category", nrow = 2) +
  tm_layout(main.title = "Conflict Distribution by Category",
            legend.outside = TRUE,
            frame = FALSE)
```

```{r}

# Define the Model Formula using original names
formula_mod <- log_fatalities ~ Political.Violence.Frequency + 
               Air.drone.strike..Sub.event. + 
               Shelling.artillery.missile.attack..Sub.event.

# 1. Base OLS Model
ols_model <- lm(formula_mod, data = sf_data)
summary(ols_model)

# 2. Lagrange Multiplier Tests for selecting SAR vs SEM
lm_tests <- lm.LMtests(ols_model, listw_knn, test = "all")
print(lm_tests)

# 3. Spatial Error Model (SEM)
sem_model <- errorsarlm(formula_mod, data = sf_data, listw = listw_knn)
summary(sem_model)

# 4. Spatial Lag Model (SAR)
sar_model <- lagsarlm(formula_mod, data = sf_data, listw = listw_knn)
summary(sar_model)

# 5. Spatial Durbin Model (SDM)
# Tests if neighbor's X variables affect your Y
sdm_model <- lagsarlm(formula_mod, data = sf_data, listw = listw_knn, type = "mixed")
summary(sdm_model)

# 6. Spatial Durbin Error Model (SDEM)
# Tests if neighbor's X variables affect your Y, with local error clustering
sdem_model <- errorsarlm(formula_mod, data = sf_data, listw = listw_knn, etype = "emixed")

summary(sdem_model)



```

```{r}
# 1. The New Base OLS Model
# OLS Model: Predicting Civilian Targeting
ols_collateral <- lm(Civilian.targeting ~ Air.drone.strike..Sub.event. + 
                       Battles..Event. + 
                       Explosions.Remote.violence..Event. +
                       fatalities, 
                     data = sf_data)

print(" Civilian Targeting ---")
summary(ols_collateral)

```

Result: The $p$-value (0.0032) is highly statistically significant, and the Moran's I statistic is positive. So, reject the null hypothesis of spatial randomness. Air and drone strikes exhibit significant positive spatial autocorrelation, meaning they are geographically clustered. Where airstrikes happen, neighboring areas are also highly likely to experience them.


: Reinforcing earlier findings, air/drone strikes have a highly significant negative relationship (Estimate = -0.17) with civilian targeting.`

General remote violence and explosions (like shelling, IEDs, or mortar fire) is the strongest driver of civilian targeting (Estimate = 0.48). T

```{r}
#Spatial Diagnostics (Lagrange Multiplier Tests) for Civilian Targeting
print("--- Spatial Diagnostics: Civilian Targeting ---")
lm.RStests(ols_collateral, listw_knn, test = "all")
```

This indicates that the geographic clustering of civilian targeting isn't a direct "contagion" effect where violence spills from one specific coordinate to the next. Instead, the clustering is driven by unobserved regional variables—likely the presence of specific armed groups operating within a broader territorial zone, local ethnic or political demographics, or regional instability that crosses arbitrary boundaries.




```{r execute-gwr, cache=TRUE, message=FALSE, warning=FALSE}
# 1. Load Necessary Libraries
library(sf)
library(ggplot2)
library(dplyr)
library(geodata)
library(GWmodel)
library(tmap)

# ---------------------------------------------------
# 2. DATA PREPARATION 
# ---------------------------------------------------
sf_data <- sf_data %>%
  mutate(fatality_group = case_when(
    fatalities >= 100 ~ "100+",
    fatalities >= 50  ~ "50-100",
    fatalities >= 20  ~ "20-50",
    fatalities > 0    ~ "1-20",
    TRUE              ~ "0"
  )) %>%
  mutate(fatality_group = factor(fatality_group, 
                                 levels = c("100+", "50-100", "20-50", "1-20", "0")))

# ---------------------------------------------------
# 3. GEOGRAPHICALLY WEIGHTED REGRESSION (GWR)
# ---------------------------------------------------
sp_data <- as(sf_data, "Spatial")

formula_mod <- log_fatalities ~ Political.Violence.Frequency + 
               Air.drone.strike..Sub.event. + 
               Shelling.artillery.missile.attack..Sub.event.

bw_adaptive <- bw.gwr(
  formula_mod, 
  data = sp_data, 
  approach = "AICc", 
  kernel = "bisquare", 
  adaptive = TRUE
)

gwr_mod <- gwr.basic(
  formula_mod, 
  data = sp_data, 
  bw = bw_adaptive, 
  kernel = "bisquare", 
  adaptive = TRUE
)

```

```{r}

# ---------------------------------------------------
# 4. VISUALIZATION: GWR RESULTS
# ---------------------------------------------------
gwr_sf <- st_as_sf(gwr_mod$SDF)

map_r2 <- tm_shape(myanmar_boundary) +
  tm_polygons(col = "gray95", border.col = "black") +
  tm_shape(gwr_sf) +
  tm_dots(col = "Local_R2", palette = "magma", size = 0.1, 
          style = "quantile", title = "Local R-Squared") +
  tm_layout(main.title = "GWR Model Fit", frame = FALSE)

map_airstrike_coef <- tm_shape(myanmar_boundary) +
  tm_polygons(col = "gray95", border.col = "black") +
  tm_shape(gwr_sf) +
  tm_dots(col = "Air.drone.strike..Sub.event.", palette = "-RdYlBu", 
          midpoint = 0, size = 0.1, style = "cont", 
          title = "Impact of Air Strikes") +
  tm_layout(main.title = "Impact of Air Strikes", frame = FALSE)

tmap_arrange(map_r2, map_airstrike_coef, ncol = 2)


```


```{r}
# ---------------------------------------------------
# 5. VISUALIZATION: SEVERITY BUBBLE MAP (ggplot2)
# ---------------------------------------------------
ggplot() +
  geom_sf(data = myanmar_boundary, fill = "gray95", color = "black", linewidth = 0.3) +
  geom_sf(data = sf_data, aes(color = fatality_group), size = 1.3, alpha = 0.8) +
  scale_color_manual(
    values = c("100+" = "#c20010", "50-100" = "#FF1493", 
               "20-50" = "#000080", "1-20" = "#FFA500", "0" = "#98fb98"),
    name = "Fatalities"
  ) +
  labs(title = "Conflict Fatalities Across Myanmar", 
       subtitle = "Fatalities categorized by severity") +
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    legend.title = element_text(size = 12, face = "bold"),
    legend.key.size = unit(0.8, "cm"),
    panel.grid = element_blank()
  ) +
  guides(color = guide_legend(override.aes = list(shape = 15, size = 5, alpha = 1)))
```






```{r}

# Load the required libraries
library(sf)
library(viridis)
library(gstat)   # CRITICAL: This package contains the idw() function
library(sp)      # Crucial for converting to Spatial/SpatialPoints and using spplot


bbox <- st_bbox(sf_data)
grid_pixels <- st_make_grid(st_as_sfc(bbox), cellsize = 0.1, what = "centers")
grid <- as(st_as_sf(grid_pixels), "Spatial") 

gridded(grid) <- TRUE 

# 2. Convert sf_data to an sp object
spatial_points <- as(sf_data, "Spatial")

# 3. Run IDW with higher power for sharper clusters (idp = 3)
idw_res <- idw(log_fatalities ~ 1, spatial_points, grid, idp = 3)

# 4. Advanced Plotting with Viridis Magma scale
spplot(idw_res, "var1.pred", 
       main = "Myanmar Conflict Intensity: IDW Analysis",
       col.regions = magma(100), 
       at = seq(0, max(sf_data$log_fatalities, na.rm = TRUE), length.out = 100),
       scales = list(draw = TRUE),
       colorkey = list(space = "right", title = "Log(Fatalities)"))


```



```{r}

library(ggplot2)

# --- 1. Distribution Plot (Histogram) ---
ggplot(df, aes(x = fatalities)) +
  geom_histogram(fill = "darkred", bins = 50) +
  scale_y_log10() +
  labs(title = "Log-Scaled Frequency of Fatalities", x = "Fatalities", y = "Count (Log)")

# --- 2. Event Type Pie Chart ---
event_summary <- colSums(df[, c("Battles..Event.", "Explosions.Remote.violence..Event.", "Violence.against.civilians..Event.")], na.rm = TRUE)
pie(event_summary, labels = names(event_summary), col = rainbow(3), main = "Major Event Distribution")


# --- 3. Fixed Barplot Code ---
# CRITICAL FIX: Explicitly sum your sub-event columns from 'df' first
sub_events <- colSums(df[, c(
  "Air.drone.strike..Sub.event.", 
  "Attack..Sub.event.", 
  "Shelling.artillery.missile.attack..Sub.event."
)], na.rm = TRUE)

# Create the dataframe using the summarized values
sub_df <- data.frame(
  Type = c("Air/Drone", "General Attack", "Shelling/Missile"),
  Count = as.numeric(sub_events)
)

# Render the horizontal bar chart
ggplot(sub_df, aes(x = reorder(Type, Count), y = Count)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() + 
  theme_minimal() +
  labs(title = "Frequency of Combat Tactics", x = "", y = "Count") +
  theme(axis.text.y = element_text(size = 10))

```

```{r}
library(GWmodel)
library(sp)
library(RColorBrewer)
```

```{r}
# GWR requires an SP object (you already converted sf_data to sp for IDW, let's do it cleanly here)
sp_data <- as(sf_data, "Spatial")

# We use the same formula you defined earlier:
formula_mod <- log_fatalities ~ Political.Violence.Frequency + Air.drone.strike..Sub.event. + Shelling.artillery.missile.attack..Sub.event.

# Calculate optimal adaptive bandwidth based on AICc
print("Calculating optimal bandwidth")
bw_adaptive <- bw.gwr(
  formula_mod, 
  data = sp_data, 
  approach = "AICc", 
  kernel = "bisquare", 
  adaptive = TRUE
)

print(paste("Optimal adaptive bandwidth (number of nearest neighbors):", bw_adaptive))
```
```{r}
# Run the Geographically Weighted Regression
gwr_mod <- gwr.basic(
  formula_mod, 
  data = sp_data, 
  bw = bw_adaptive, 
  kernel = "bisquare", 
  adaptive = TRUE
)

# Print a summary of the GWR model
print(gwr_mod)

# Compare the Global R-squared (from OLS) to the GWR R-squared
print(paste("Global OLS R-Squared:", round(summary(ols_model)$r.squared, 3)))
print(paste("GWR Adjusted R-Squared:", round(gwr_mod$GW.diagnostic$gw.R2, 3)))
```

```{r}

library(tmap)

# Extract the SpatialDataFrame containing local coefficients and convert back to 'sf'
gwr_sf <- st_as_sf(gwr_mod$SDF)

# 1. Map of Local R-Squared (Where does the model explain the most variance?)
map_r2 <- tm_shape(myanmar_boundary) +
  tm_polygons(col = "#fdfdfd", border.col = "black") +
  tm_shape(gwr_sf) +
  tm_dots(
    col = "Local_R2", 
    palette = "magma", 
    size = 0.5, 
    style = "quantile",
    title = "Local R-Squared"
  ) +
  tm_layout(main.title = "GWR Model Fit (Local R-Squared)", frame = FALSE)

# 2. Map of Local Coefficient: Air & Drone Strikes 
# (Where are airstrikes most strongly correlated with fatalities?)
map_airstrike_coef <- tm_shape(myanmar_boundary) +
  tm_polygons(col = "#fdfdfd", border.col = "black") +
  tm_shape(gwr_sf) +
  tm_dots(
    col = "Air.drone.strike..Sub.event.", 
    palette = "-RdYlBu", # Diverging palette (negative to positive)
    midpoint = 0,        # Center the color scale on 0
    size = 0.5, 
    style = "cont",
    title = "Air Strike Coefficient"
  ) +
  tm_layout(main.title = "Local Impact of Air Strikes on Fatalities", frame = FALSE)

# Display the maps side-by-side
tmap_arrange(map_r2, map_airstrike_coef, ncol = 2)

```

```{r}

library(knitr)
library(dplyr)

# 3. COMPILING COMPARISON METRICS MATRIX
# ==============================================================================

# Function to extract standard global parametric model features
get_metrics <- function(model, name) {
  data.frame(
    Model = name,
    AIC = AIC(model),
    Log_Likelihood = as.numeric(logLik(model)),
    df = attr(logLik(model), "df")
  )
}

# Compile standard global models using the metric extractor
global_results <- rbind(
  get_metrics(ols_model, "OLS (Baseline)"),
  get_metrics(sar_model, "SAR (Spatial Lag)"),
  get_metrics(sem_model, "SEM (Spatial Error)"),
  get_metrics(sdm_model, "SDM (Spatial Durbin)"),
  get_metrics(sdem_model, "SDEM (Spatial Durbin Error)")
)

# Extract Local GWR metrics safely to bypass structural constraints
# (GWR has no direct log-likelihood metric, so we label it NA)
gwr_metrics <- data.frame(
  Model = "GWR (Geographically Weighted)",
  AIC = gwr_mod$GW.diagnostic$AICc, 
  Log_Likelihood = NA,               
  df = gwr_mod$GW.diagnostic$edf     
)

# Merge global regression rows and local GWR data row together 
comparison_results <- rbind(global_results, gwr_metrics)


# ==============================================================================
# 4. ORDER AND DISPLAY RESULTS
# ==============================================================================
# Sort rows based on model efficiency (Lower AIC is superior fit)
comparison_results <- comparison_results %>% arrange(AIC)

# Generate clear summary grid display
kable(comparison_results, 
      caption = "Comprehensive Model Fit Summary Matrix (Sorted by Best AIC Score)", 
      digits = 2)
```


```{r}

ggplot(comparison_results, aes(x = reorder(Model, AIC), y = AIC, fill = Model)) +
  # Create the bar elements
  geom_bar(stat = "identity", width = 0.65, color = "white", lwd = 0.3) +
  
  # Add exact AIC value labels at the end of each bar
  geom_text(aes(label = format(round(AIC, 1), nsmall = 1)), 
            hjust = -0.15, size = 3.5, fontface = "bold") +
  
  # Flip coordinates to horizontal for perfect readability of model names
  coord_flip() +
  
  # Apply a high-contrast color palette (Viridis Mako or Plasma works great)
  scale_fill_viridis_d(option = "plasma", end = 0.85) +
  
  # Expand the y-axis (which is technically the AIC axis now) so labels aren't cut off
  scale_y_continuous(expand = expansion(mult = c(0, 0.15))) +
  
  # Labels and text headings
  labs(
    title = "Model Performance Comparison (AIC Scores)",
    subtitle = "Lower AIC scores indicate a superior balance of model fit and parsimony",
    x = "",
    y = "Akaike Information Criterion (AIC)"
  ) +
  
  # Clean, minimal aesthetic theme adjustments
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold", size = 14, margin = margin(b = 5)),
    plot.subtitle = element_text(color = "gray40", size = 10, margin = margin(b = 15)),
    axis.text.y = element_text(face = "bold", size = 10, color = "black"),
    axis.text.x = element_text(size = 9),
    panel.grid.major.y = element_blank(), # Remove horizontal lines since bars define space
    panel.grid.minor = element_blank(),
    legend.position = "none" # Hide legend since the y-axis labels identify the models
  )

```


```{r}

library(tmap)
library(sf)

# 1. Convert your GWR Spatial Data Frame output into a modern sf object
gwr_sf <- st_as_sf(gwr_mod$SDF)

# 2. Plot the Local R2 surface map
map_r2 <- tm_shape(gwr_sf) +
  tm_dots(fill = "Local_R2", 
          fill.scale = tm_scale_continuous(values = "viridis"),
          title = "Local R² Value") +
  tm_layout(main.title = "GWR Model Performance: Shifting Local R²", 
            main.title.position = "center")

# 3. Plot the Local Impact (Coefficient) of Air/Drone Strikes
map_coef_air <- tm_shape(gwr_sf) +
  tm_dots(fill = "Air.drone.strike..Sub.event.", # Use exact column name from your GWR output
          fill.scale = tm_scale_continuous(values = "rd_yl_bu", midpoint = 0),
          title = "Airstrike Coefficient") +
  tm_layout(main.title = "Localized Lethal Impact of Air Warfare", 
            main.title.position = "center")

# Print the maps
print(map_r2)
print(map_coef_air)

```